\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Add figures

\newcommand{\zbf}{Zauberfl\"{o}te\xspace}
\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
\newcommand{\inclfigure}[3]{
    \begin{figure}
        \begin{centering}
            \includegraphics[width=.8\linewidth]{#2}
            \caption{#3}
            \label{#1}
        \end{centering}
    \end{figure}
}

@@

\section{Introduction}
It is common for personal blogs and other small websites to gain sudden attention
on large, high-traffic websites such as Reddit. Since these websites usually
experience much smaller traffic loads, the hardware devoted to hosting them
is typically not powerful enough to cope with this large influx of content requests.
These sudden, unexpected bursts of traffic often result in websites loading at
extremely slow speeds, or not loading at all, and is colloquially known as the
"reddit hug of death" or the "reddit effect." \\

@@

The \zbf architecture consists of several loosely-connected components (see
figure~\ref{fig:components}). At the highest level, there is a download manager that
provides a reliable download service. It relies on the tracker interface and
the connection manager. The tracker interface facilitates communication with
the central tracker for information about peers and file sizes, and the
connection manager provides an interface for peer-to-peer message transfer. \\

@@

\inclfigure{fig:components}{components.pdf}{
    Relationship between different client-side components of the \zbf
    peer-to-peer download service. Components in gray are standard browser
    APIs.
}

@@

\subsection{Simulating the "reddit effect"}
Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the "reddit effect" by throttling the content delivery
bandwidth of the central server hosting the desired resource. We limited the content delivery
rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf
against the HTTP content delivery latency under the throttled bandwidth conditions.

@@

\subsection{Results}
 % TODO

@@

\begin{figure}[heatmap.pdf]
% TODO: heatmap here
\caption{Average page load time over P2P for seeders vs leechers}
\end{figure}

As seen in figure 1, the performance of \zbf depended on the seeder-to-leecher ratio.
In general, the lowest latency in load time was achieved when the seeder-to-leecher
ratio was highest. However, the system performed well in any condition with many
seeder peers, reflecting the performance benefits provided by chunking of resources
and parallelization of sending chunks. The system performed worst when there were many
leechers and only a few seeders.

\subsubsection{\zbf vs HTTP}
% TODO: figure out ratio of seeders to leechers
Our next empirical analysis was to keep the ratio of seeders to leechers constant at X,
and compare the page load times for a throttled HTTP server vs \zbf as we increase the
number of users attempting to concurrently load the page.

\begin{figure}[lineplot.pdf]
% TODO: other plot here
% TODO: figure out ratio of seeders to leechers
\caption{Average page load time over P2P compared to HTTP on throttled server assuming
constant ratio of X seeders per leecher}
\end{figure}

As seen in figure 2, \zbf performed well in comparison to loading content over HTTP.
While both experienced increases in content delivery latency with increasing numbers
of peers requesting content, in general \zbf had lower latency than HTTP. Note
that our simulated "reddit effect" implies hundreds of thousands of other
simultaneous connection; however, since we are simulating the effect, these
imaginary peers cannot distribute content to new peers. So, \zbf could potentially
provide an even greater latency drop with more active seeding peers, which would
be the case in a real-world scenario.

>>>>

\newcommand{\zbf}{Zauberfl\"{o}te\xspace}
\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
\newcommand{\inclfigure}[4]{
    \begin{figure}
        \begin{centering}
            \includegraphics[angle=#3,width=.8\linewidth]{#2}
            \caption{#4}
            \label{#1}
        \end{centering}
    \end{figure}
}

@@

\section{Introduction}
It is common for personal blogs and other small websites to gain sudden attention
on large, high-traffic websites such as Reddit. Since these websites usually
experience much smaller traffic loads, the hardware devoted to hosting them
is typically not powerful enough to cope with this large influx of content requests.
These sudden, unexpected bursts of traffic often result in websites loading at
extremely slow speeds, or not loading at all, and is colloquially known as the
``reddit hug of death'' or the ``reddit effect.'' \\

@@

The \zbf architecture consists of several loosely-connected components (see
\Cref{fig:components}). At the highest level, there is a download manager that
provides a reliable download service. It relies on the tracker interface and
the connection manager. The tracker interface facilitates communication with
the central tracker for information about peers and file sizes, and the
connection manager provides an interface for peer-to-peer message transfer. \\

@@

\inclfigure{fig:components}{components.pdf}{0}{
    Relationship between different client-side components of the \zbf
    peer-to-peer download service. Components in gray are standard browser
    APIs.
}

@@

\subsection{Simulating the ``reddit effect''}
Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the ``reddit effect'' by throttling the content delivery
bandwidth of the central server hosting the desired resource. We limited the content delivery
rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf
against the HTTP content delivery latency under the throttled bandwidth conditions.

@@

\subsection{Results}

@@

\inclfigure{fig:heatmap}{heatmap.eps}{-90}{
    Average page load time over P2P for seeders vs leechers.
}

As seen in \Cref{fig:heatmap}, the performance of \zbf depended on the
seeder-to-leecher ratio. In general, the lowest latency in load time was
achieved when the seeder-to-leecher ratio was highest. However, the system
performed well in any condition with many seeder peers, reflecting the
performance benefits provided by chunking of resources and parallelization of
sending chunks. The system performed worst when there were many leechers and
only a few seeders.

\subsubsection{\zbf vs HTTP}

Our next empirical analysis was to keep the ratio of seeders to leechers
constant at 1, and compare the page load times for a throttled HTTP server vs
\zbf as we increase the number of users attempting to concurrently load the
page.

\inclfigure{fig:scalability}{scalability.eps}{-90}{
    Average page load time over P2P compared to HTTP on throttled server
    assuming constant ratio of 1 seeder per leecher.
}

As seen in \Cref{fig:scalability}, \zbf performed well in comparison to
loading content over HTTP. While both experienced increases in content delivery
latency with increasing numbers of peers requesting content, in general \zbf
had lower latency than HTTP. Note that our simulated ``reddit effect'' implies
hundreds of thousands of other simultaneous connection; however, since we are
simulating the effect, these imaginary peers cannot distribute content to new
peers. So, \zbf could potentially provide an even greater latency drop with
more active seeding peers, which would be the case in a real-world scenario.
